Artistic Curve Steganography with Musical Audio As A Carrier

### 2022-10-30 writeup/paper.tex
Some more work on the technique writeup

@@

Let $T = (T_1, T_2, \hdots, T_N \}$ the desired Euclidean ``target'' point sequence to embed, where each $T_i \in \mathbb{R}^d$, and let $x$ be a set of $N$ audio samples which will serve as a carrier.  The goal is to perturb the samples of $x$ so that some function of $x$ matches $T$ as closely as possible.

@@

\subsection{Recovering Component Scales}

@@

\section{Experiments}

>>>>

Satisfying goals 1 and 2 simultaneously is the biggest challenge of this work.

@@

Let $T = (T_1, T_2, \hdots, T_N \}$ the desired Euclidean target point sequence to hide, where each $T_i \in \mathbb{R}^d$, and let $x$ be a set of $N$ audio samples which will serve as a carrier.  The goal is to perturb the samples of $x$ so that some function of $x$ matches $T$ as closely as possible.  The function we choose is based on a ``time regularized'' version of the magnitude Short-Time Fourier Transform (STFT) which we call a {\em sliding window sum} STFT (SWS-STFT).  As a first step, we compute a {\em non-overlapping} short-time Fourier Transform based on a chosen window length $w$:

\begin{equation}
  S_{j, k} = \sum_{n = 0}^w x_{jw + n} e^{-i 2 \pi k n / w}
\end{equation}

with a total of $N$ frames.  Then, given a second window length $\ell$, we compute the following {\em sliding window sum} $X$ of the magnitudes of $|S_{j, k}|$

\begin{equation}
  X_{j, k} = \sum_{n = 0}^{\ell-1} |S_{j+n, k}|
\end{equation}

nonnegative least squares

A crucial step to keep the hidden signal imperceptible is to rescale the targets to match the dynamic range of the signals.  Unfortunately, we lose relative scale information between the components, but we will explain how to store and recover this in Section~\ref{sec:componentscales}

\subsubsection{The choice of non-overlapping windows}
Though some other works use transforms with overlapping windows (e.g. \cite{hwan_sik_yun_acoustic_2010}), we find that changing different STFT bins independently can lead to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.  An algorithm like Griffin-Lim \cite{griffin1984signal} can recover a signal whose spectrogram has a locally minimal distance to the perturbed STFT, but we find that this step introduces an unacceptable level of distortion both in the target and the carrier audio.  This problem occurs even for real-valued transforms such as the Discrete Cosine Transform (which was used by \cite{geleta_pixinwav_2021}).  We sidestep this problem completely by using non-overlapping windows as in \cite{xiaoxiao_dong_data_2004}.

The main downside of non-overlapping windows is that they lead to fewer STFT frames.  For instance, for a 30 second audio clip at 44100hz using a window length of 1024, we are limited to about 1292 frames, which is half of what we would get using an overlapping STFT with a hop length of 512.  However, a quick thought experiment shows that this is still a reasonable rate.  Suppose that we use a sliding window length $\ell=16$, for a total of 1277 carrier samples.  Suppose also that the precision of our embedding of a 2D plane curve is roughly on par with an 8 bit per coordinate quantization in a more traditional binary encoding scheme.  Then the total number of bits transmitted over 30 seconds is $1277 \times 8 \times 2$, or about 681 bits/second.  This number jumps to about 1022 bits/second for a 3D curve.  These numbers are on part with other recent techniques that are designed to be robust to noise (e.g. 900 bits/second in the OFDM technique of \cite{eichelberger_receiving_2019}).

@@

In general, the SWS-STFT sequence $X$ will not have the same number of samples as the target $T$.  If we stick to scenarios where $T$ has more samples, we can index $X$ by a default function

Our use of the Viterbi algorithm for re-parameterizing geometric sequences is related to the technique for corpus-based concatenative synthesis presented by the authors of \cite{schwarz2007corpus}.

As a rule of thumb, we find that having a target curve with about 1.5-2x as many samples as there are SWS-STFT frames gives enough wiggle room for the Viterbi algorithm.  Therefore, in our experiments in Section~\ref{sec:experiments}, we will generate TSP and Hamiltonian sequences with 2000 samples for our 1200-1300 SWS-STFT frames

\subsection{Storing Component Scales in Phase}
\label{sec:componentscales}

We use the technique presented by the authors of \cite{xiaoxiao_dong_data_2004} to recover the scales of each component.

@@

\section{Experiments}
\label{sec:experiments}
